---
title: "Predictive distributions of outstanding liabilities in general insurance"
output: html_document
---
<br>

*This code is provided by Peter England on behalf of EMC Actuarial and Analytics Ltd as an educational resource.* <br><br>

R code to reproduce the tables in:

England & Verrall (2006). Predictive distributions of outstanding liabilities in general insurance. __Annals of Actuarial Science__, 1, II, 221-270. https://doi.org/10.1017/S1748499500000142

The paper shows how predictive distributions of outstanding liabilities in general insurance can be obtained using bootstrap or 'Bayesian' MCMC techniques for clearly defined statistical models.

The code supports Mack's model, the Over-dispersed Poisson model, and the Over-dispersed Negative Binomial model.

Select which model to apply using the "method" variable below.

A commentary of the results is provided in the paper.<br><br>

### Import libraries, stochastic reserving functions and data, and look at the data:

```{r, message=FALSE, warning=FALSE}
# for tables 
options(width=200)

## Set up libraries
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(rstan)) # for MCMC sampling
#library(shinystan) # for diagnostics after fitting MCMC models
suppressPackageStartupMessages(library(tidyverse)) # for graphs #masks rstan::extract()
suppressPackageStartupMessages(library(ggfan)) # For fan charts

# Read in stochastic reserving functions
source("StochResFunctions.R")

# Read in data from csv file
TA <- read.table("TandA.csv", sep=",")

# Select triangle to work on
Triangle <- TA

# Look at data first
# Incremental claims data:
Inc_Triangle <- Incrementals(Triangle)
print("Incremental Amounts")
Inc_Triangle
print("Cumulative Amounts")
#Triangle <- Cumulatives(Inc_Triangle)
Triangle

# Incremental claims data:
plotTriangleGraph(Inc_Triangle)

# Cumulative claims data
plotTriangleGraph(Triangle)

# Set Mask for exclusion of link ratios (if required)
# Exclusions only work when bootstrapping; exclusions have not been set up for the MCMC models
Indicators <- matrix(1,nrow(Triangle)-1, ncol(Triangle)-1)
#Indicators[4,3] <- 0

```
<br><br>

### Obtain link ratios and volume-weighted chain ladder factors:

```{r, message=FALSE}
# Calculate link ratio triangle and volume-weighted chain ladder factors
LRs <- LR_Tri(Triangle)
CL_facs <- CL_factors(LRs$LRs, LRs$Weight)

print("Triangle of link ratios")
LRs$LRs

print("Chain ladder factors")
CL_facs
plotLRsGraph(LRs$LRs)
```
<br><br>

### Fit a basic chain ladder model:

```{r}
# Calculate volume-weighted chain ladder results
CL_Result <- Tri_forecast(Triangle, CL_facs)
Latest_by_yr <- CL_Result$Latest
TotalLatest <- sum(Latest_by_yr)
Latest <- c(Latest_by_yr, TotalLatest)
Reserves_by_yr <- CL_Result$Reserves
TotalReserve <- CL_Result$TotalReserve
Reserves <- c(Reserves_by_yr, TotalReserve)
Ultimates_by_yr <- CL_Result$Ultimates
TotalUltimate <- sum(Ultimates_by_yr)
Ultimates <- c(Ultimates_by_yr, TotalUltimate)

Table_0 <- cbind(round(Latest,0), round(Reserves,0), round(Ultimates,0))
dimnames(Table_0) <- list(c(1:length(Triangle), "Total"), c("Latest", "Reserves", "Ultimates"))
names(dimnames(Table_0)) <- c("Year","Chain Ladder Results")
print(Table_0)
```
<br><br>

## MAIN RESULTS FROM THE PAPER:<br>

### Select which model to use, obtain analytic (closed form) results, then apply bootstrap and MCMC methods:

```{r}
##
## Model settings for Bootstrapping and MCMC methods:
# method = "Mack", "ODPConstant", "ODPNonConstant", "NegBinConstant", or "NegBinNonConstant"
# (For ODP and NegBin, "NonConstant" is usually more appropriate)
# seed = seed point for random number generator (if blank, it is different each time)

## Bootstrap specific settings:
# Bstrap_iterations = number of bootstrap replications
# BootstrapDist = "NP" for non-parametric, or "Gamma" or "Lognormal" for parametric (this is for the pseudo_data distribution)
# ForecastDist = "NP" for non-parametric, or "Gamma" or "Lognormal" for parametric (this is for the process distribution)

## MCMC specific settings:
# MCMC_iterations = number of MCMC replications (after exclusion of burn-in samples)
# chains = number of MCMC chains
# ForecastDist = "NP" for non-parametric, or "Gamma" or "Lognormal" for parametric (this is for the process distribution)

## Select model:
method <- "ODPConstant"
#method <- "ODPNonConstant"
#method <- "NegBinConstant"
#method <- "NegBinNonConstant"
#method <- "Mack"

seed <- 1234 # seed point for MCMC and Bootstrap

# Bootstrap settings
Bstrap_iterations <- 10000 # number of Bootstrap iterations
#
BootstrapDist = "NP" # non-parametric bootstrapping
#BootstrapDist = "Gamma" # generating pseudo-data with Gamma distribution
#BootstrapDist = "Lognormal" # generating pseudo-data with Lognormal distribution
#
#ForecastDist <- "NP" # non-parametric forecasting
ForecastDist <- "Gamma" # forecasting with Gamma distribution
#ForecastDist <- "Lognormal" # forecasting with Lognormal distribution

# MCMC settings
parallel::detectCores()
#
MCMC_iterations <- Bstrap_iterations # target total number of MCMC iterations across all chains after burn-in
chains <- 4 # number of MCMC chains
MCMC_iter <- 2*MCMC_iterations/chains # number of MCMC iterations for each chain. Note 50% are used for burn-in and discarded
#
ForecastDist <- ForecastDist # set above

## Analytic result
Analytic_Result <- Analytic_RMSEPs(Triangle, method, Mask=Indicators)

## Bootstrap and MCMC
# Set user-defined sqrtScale (sigmas for Mack's model) if required
# This can be used to control variability at the forecasting stage
# (Not required to reproduce methods used in the paper)
UserSqrtScale <- NULL

## Bootstrap result
Bstrap_Result <- Run_Bootstrap(Triangle, Mask=Indicators, method=method, 
                               replications=Bstrap_iterations, seed=seed, BootstrapDist=BootstrapDist, 
                               ForecastDist=ForecastDist, UserSqrtScale=UserSqrtScale)

## MCMC result
message("Compiling MCMC model in Stan. Please wait...")
MCMC_Result <- Run_MCMC(Triangle, method=method, replications=MCMC_iter, chains=chains, seed=seed,
                        ForecastDist=ForecastDist, UserSqrtScale=UserSqrtScale)
```
<br><br>

## Summarise Results<br>

### Parameter estimates and standard errors:

```{r}
ML_coefs <- Analytic_Result$coefs
ML_parameter_se <- Analytic_Result$parameter_se

MCMC_params <- rstan::extract(MCMC_Result$MCMCfit)
MCMC_Coef_Means <- apply(MCMC_params$coefs, 2, mean)
MCMC_Coef_SDs <- apply(MCMC_params$coefs, 2, sd)

Table_2 <- cbind(round(ML_coefs,3), round(ML_parameter_se,3), round(MCMC_Coef_Means,3), round(MCMC_Coef_SDs,3))
dimnames(Table_2) <- list((dimnames(Table_2)[[1]]), c("ML Est.", "ML S.E.", "MCMC Mean", "MCMC SD"))
sqrtScale <- Bstrap_Result$Resids$sqrtScale
dp_labels <- paste("DP", 1:length(sqrtScale), sep=" ")
Scale_by_DevPeriod <- cbind(round(sqrtScale,1), round(sqrtScale^2))
dimnames(Scale_by_DevPeriod) <- list(dp_labels, c("Sqrt(Scale)", "Scale"))

message(paste0(method,"\n","Parameter estimates and standard errors"))
Table_2
Scale_by_DevPeriod
```
<br><br>

### Analytic results:

```{r}
Res <- c(Analytic_Result$Reserves, Analytic_Result$TotalReserves)
Res_SD <- c(Analytic_Result$Reserves_SD, Analytic_Result$TotalReserve_SD)
Res_CoV <- c(Analytic_Result$Reserves_CoV, Analytic_Result$TotalReserve_CoV)
Table_3 <- cbind(round(Res,0), round(Res_SD,0), round(100*Res_CoV,1))
dimnames(Table_3) <- list(c(1:length(Triangle), "Total"), c("CL Reserves", "Reserve SD", "Reserve CoV %"))
names(dimnames(Table_3)) <- c("Year","Analytic")

message(paste0(method,"\n","Parameter estimates and standard errors"))
Table_3
```
<br><br>

### MCMC and Bootstrap Summary:

```{r}
Table_4 <- cbind(round(MCMC_Result$Avg_Reserve), round(MCMC_Result$SD_Reserve), round(100*MCMC_Result$CoV_Reserve,1), 
                 round(Bstrap_Result$Avg_Reserve), round(Bstrap_Result$SD_Reserve), round(100*Bstrap_Result$CoV_Reserve,1))
Table_4_Totals <- cbind(round(MCMC_Result$Avg_TotalReserve), round(MCMC_Result$SD_TotalReserve), round(100*MCMC_Result$CoV_TotalReserve,1), 
                        round(Bstrap_Result$Avg_TotalReserve), round(Bstrap_Result$SD_TotalReserve), round(100*Bstrap_Result$CoV_TotalReserve,1))
Table_4 <- rbind(Table_4, Table_4_Totals)
dimnames(Table_4) <- list(c(1:length(Triangle), "Total"), c("MCMC Avg Reserves", "MCMC SD", "MCMC CoV %", "Bstrap Avg Reserves", "Bstrap SD", "Bstrap CoV %"))
names(dimnames(Table_4)) <- c("Year","Simulated (Undiscounted)")

message(paste0(method,"\n","MCMC and Bootstrap Summary"))
Table_4
```
<br><br>

### Show set of summary statistics from MCMC results:

```{r}
message(paste0(method,"\n","Bayesian Summary Statistics"))
Table_5_MCMC <- ShowSummaryStats(MCMC_Result, Output="Reserves")
```
<br><br>

### Show set of summary statistics from bootstrap results:

```{r}
message(paste0(method,"\n","Bootstrap Summary Statistics"))
Table_5_Bstrap <- ShowSummaryStats(Bstrap_Result, Output="Reserves")
```
<br><br>

### Residual graphs:

```{r, message=FALSE}
# Residuals graphs associated with method
#plotResiduals(Bstrap_Result$Resids, resid_type="adjunscaledresids", bstrap_method=method)
plotResiduals(Bstrap_Result$Resids, resid_type="zeroavgscaledresids", bstrap_method=method)

```
<br><br>

### Bootstrap results: Histogram and reserve development (fan) graphs:

```{r, message=FALSE}
## Bootstrap Graphs
# Histograms - Bootstrap undiscounted reserves
plotHistogram_Total(Bstrap_Result$TotalReserve)
#plotHistogram_by_yr(Bstrap_Result$Reserves)

# Development graphs
BStrap_Cumulatives <- Bstrap_Result$Cumulatives
for (yr in seq(2, ncol(BStrap_Cumulatives), by = 2)) {
  print(plotDevelopmentGraph(BStrap_Cumulatives,yr))
}
```
<br><br>

### MCMC results: Histogram and reserve development (fan) graphs:

```{r, message=FALSE}
## MCMC Graphs
# Histograms - Bayesian undiscounted reserves
plotHistogram_Total(MCMC_Result$TotalReserve)
#plotHistogram_by_yr(MCMC_Result$Reserves)

# Development graphs - Bayesian
MCMC_Cumulatives <- MCMC_Result$Cumulatives
for (yr in seq(2, ncol(MCMC_Cumulatives), by = 2)) {
  print(plotDevelopmentGraph(MCMC_Cumulatives,yr))
}
```


