---
title: "On the lifetime and one-year views of reserve risk, with application to IFRS 17 and Solvency II risk margins"
output: html_document
---
<br>

*This code is provided by Peter England on behalf of EMC Actuarial and Analytics Ltd as an educational resource.* <br><br>

R code to reproduce the tables in:

England, Verrall & Wüthrich (2018/2019). On the lifetime and one-year views of reserve risk, with application to IFRS 17 and Solvency II risk margins. __Insurance: Mathematics and Economics (2019)__ https://doi.org/10.1016/j.insmatheco.2018.12.002

Pre-print version available from __SSRN (2018)__ https://ssrn.com/abstract=3141239

The paper brings together analytic and simulation-based approaches to reserve risk in general (P&C) insurance, applied to the traditional actuarial view of risk over the lifetime of the liabilities and to the one-year view of Solvency II. It also connects the lifetime and one-year views of risk. Predictive distributions are used to estimate risk margins under Solvency II and risk adjustments under IFRS 17.

The code supports Mack's model (as used in the paper), the Over-dispersed Poisson model, and the Over-dispersed Negative Binomial model.

Select which model to apply using the "method" variable below.

A commentary of the results is provided in the paper.
<br><br>

### Import libraries, stochastic reserving functions and data, and look at the data:

```{r, message=FALSE, warning=FALSE}
# for tables 
options(width=200)

## Set up libraries
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ChainLadder)) # for Merz-Wuthrich analytic SD of CDR
suppressPackageStartupMessages(library(tidyverse)) # for graphs
suppressPackageStartupMessages(library(ggfan)) # for fan charts

# Read in stochastic reserving functions
source("StochResFunctions.R")

# Read in data from csv file
TA <- read.table("TandA.csv", sep=",")

# Select triangle to work on
Triangle <- TA

# Look at data first
# Incremental claims data:
Inc_Triangle <- Incrementals(Triangle)
print("Incremental Amounts")
Inc_Triangle
print("Cumulative Amounts")
#Triangle <- Cumulatives(Inc_Triangle)
Triangle

# Incremental claims data:
plotTriangleGraph(Inc_Triangle)

# Cumulative claims data
plotTriangleGraph(Triangle)

# Set Mask for exclusion of link ratios (if required)
Indicators <- matrix(1,nrow(Triangle)-1, ncol(Triangle)-1)
#Indicators[3,6] <- 0
```
<br><br>

### Obtain link ratios and volume-weighted chain ladder factors:

```{r}
# Calculate link ratio triangle and volume-weighted chain ladder factors
LRs <- LR_Tri(Triangle)
CL_facs <- CL_factors(LRs$LRs, LRs$Weight)

LRs$LRs
CL_facs
#plotTriangleGraph(LRs$LRs)
plotLRsGraph(LRs$LRs)
```
<br><br>

### Fit a basic chain ladder model:

```{r}
# Calculate volume-weighted chain ladder results
CL_Result <- Tri_forecast(Triangle, CL_facs)
Latest_by_yr <- CL_Result$Latest
TotalLatest <- sum(Latest_by_yr)
Latest <- c(Latest_by_yr, TotalLatest)
Reserves_by_yr <- CL_Result$Reserves
TotalReserve <- CL_Result$TotalReserve
Reserves <- c(Reserves_by_yr, TotalReserve)
Ultimates_by_yr <- CL_Result$Ultimates
TotalUltimate <- sum(Ultimates_by_yr)
Ultimates <- c(Ultimates_by_yr, TotalUltimate)

Table_0 <- cbind(round(Latest,0), round(Reserves,0), round(Ultimates,0))
dimnames(Table_0) <- list(c(1:length(Triangle), "Total"), c("Latest", "Reserves", "Ultimates"))
names(dimnames(Table_0)) <- c("Year","Chain Ladder Results")
Table_0
```
<br><br>

## MAIN RESULTS FROM THE PAPER:<br>

### Select which model to use, then apply bootstrap method and show summary statistics:

```{r}
## BOOTSTRAPPING
##
## Settings:
## method = "Mack", "ODPConstant", "ODPNonConstant", "NegBinConstant", or "NegBinNonConstant"
## (For ODP and NegBin, "NonConstant" is usually more appropriate)
## replications = number of bootstrap replications
## seed = seed point for random number generator (if blank, it is different each time)
## BootstrapDist = "NP" for non-parametric, or "Gamma" or "Lognormal" for parametric (this is for the pseudo_data distribution)
## ForecastDist = "NP" for non-parametric, or "Gamma" or "Lognormal" for parametric (this is for the process distribution)

method <- "Mack" # Mack's method was used in the paper
#method <- "ODPConstant"
#method <- "ODPNonConstant"
#method <- "NegBinConstant"
#method <- "NegBinNonConstant"

#BootstrapDist = "NP" # non-parametric bootstrapping
BootstrapDist = "Gamma" # generating pseudo-data with Gamma distribution
#BootstrapDist = "Lognormal" # generating pseudo-data with Lognormal distribution

#ForecastDist <- "NP" # non-parametric forecasting
ForecastDist <- "Gamma" # forecasting with Gamma distribution
#ForecastDist <- "Lognormal" # forecasting with Lognormal distribution

replications <- 10000
seed <- 100 # seed point for bootstrapping
#seed <- 321

## LIFETIME VIEW - Bootstrapping
# Set user-defined sqrtScale (sigmas for Mack's model) if required
# This can be used to control variability at the forecasting stage
# (Not required to reproduce methods used in the paper)
UserSqrtScale <- NULL

Bstrap_Result <- Run_Bootstrap(Triangle, Mask=Indicators, method=method, 
                               replications=replications, seed=seed, BootstrapDist=BootstrapDist, 
                               ForecastDist=ForecastDist, UserSqrtScale=UserSqrtScale)

# Show set of summary statistics from bootstrap results
ShowStats <- ShowSummaryStats(Bstrap_Result, Output="Reserves")
ShowStats <- ShowSummaryStats(Bstrap_Result, Output="Ultimates")
```

```{r, message=FALSE}
# Residuals graphs associated with bootstrap method
#plotResiduals(Bstrap_Result$Resids, resid_type="adjunscaledresids", bstrap_method=method)
plotResiduals(Bstrap_Result$Resids, resid_type="zeroavgscaledresids", bstrap_method=method)
```
<br><br>

### Bootstrap results: Histogram and reserve development (fan) graphs:

```{r, message=FALSE}
# Histograms - Undiscounted reserves
plotHistogram_Total(Bstrap_Result$TotalReserve)
#plotHistogram_by_yr(Bstrap_Result$Reserves)

# Development graphs
BStrap_Cumulatives <- Bstrap_Result$Cumulatives
for (yr in seq(2, ncol(BStrap_Cumulatives), by = 2)) {
  print(plotDevelopmentGraph(BStrap_Cumulatives,yr))
}
```
<br><br>

### Table 1: Chain ladder factors and sqrtScale  / Mack's alpha parameters

```{r}
# Table 1 - Chain ladder factors and sqrtScale  / Mack's alpha parameters
if (method %in% c("Mack", "NegBinConstant", "NegBinNonConstant")) {
  params_by_DevPeriod <- rbind(round(c(Bstrap_Result$CL_facs,1),3), round(c(Bstrap_Result$Resids$sqrtScale, NA),1))
} else {
  params_by_DevPeriod <- rbind(round(c(Bstrap_Result$CL_facs,1),3), round(Bstrap_Result$Resids$sqrtScale,1))
}
dp_labels <- paste("DP", 1:length(Triangle), sep=" ")
dimnames(params_by_DevPeriod) <- list(c("Dev Factors", "sqrtScale"), dp_labels)
cat("Development factors and sqrtScale parameters\n")
params_by_DevPeriod
```
<br><br>

### Table 2: Analytic results for chain ladder model

```{r}
# Table 2 - Analytic results for chain ladder model
Analytic_RMSEPs <- Calc_RMSEPs(Triangle, method, Mask=Indicators)
CL_Res <- Analytic_RMSEPs$CL_Res
CL_Res_SD <- Analytic_RMSEPs$Res_SD
CL_Res_CoV <- safe_divide(CL_Res_SD, CL_Res)
CL_CDR_SD_1Yr <- Analytic_RMSEPs$CDR_SD_1Yr
CL_CDR_Ratio <- safe_divide(CL_CDR_SD_1Yr, abs(CL_Res))
Table_2 <- cbind(round(CL_Res), round(CL_Res_SD), round(100*CL_Res_CoV,1),round(CL_CDR_SD_1Yr), round(100*CL_CDR_Ratio,1))
dimnames(Table_2) <- list(c(1:length(Triangle), "Total"), c("CL Reserves", "Reserve SD", "Reserve CoV %", "CDR SD", "CDR SD Ratio %"))
names(dimnames(Table_2)) <- c("Year","Analytic")
Table_2
```
<br><br>

### Table 3: RMSEPs for each future year

```{r}
# Table 3
# Analytic results for chain ladder model
# For Mack's assumptions, use Merz-Wuthrich (2014) The Full Picture, and the ChainLadder package
Table_3 <- round(Analytic_RMSEPs$CDR_SD)
if (method!="Mack") {message("Analytic CDR RMSEPs not available for ODP or NegBin models")}
Table_3
```
<br><br>

### ONE-YEAR VIEW AND BEYOND - Re-reserving using the "Actuary-in-the-box"
<br>

### Table 4: Simulation results summary

```{r}
## ONE-YEAR VIEW AND BEYOND - Re-reserving using "Actuary-in-the-box"
CDR_Result <- CDR_Full_Picture(Triangle, Bstrap_Result$Cumulatives, VAR_p=0.995, Mask=Indicators)

#Table 4 - Simulation results summary
Table_4 <- cbind(round(Bstrap_Result$Avg_Reserve), round(Bstrap_Result$SD_Reserve), round(100*Bstrap_Result$CoV_Reserve,1), 
                 round(CDR_Result$SD_CDR[1,]), round(100*safe_divide(CDR_Result$SD_CDR[1,], Bstrap_Result$Avg_Reserve),1))
Table_4_Totals <- cbind(round(Bstrap_Result$Avg_TotalReserve), round(Bstrap_Result$SD_TotalReserve), round(100*Bstrap_Result$CoV_TotalReserve,1), 
                        round(CDR_Result$SD_TotalCDR[1]), round(100*safe_divide(CDR_Result$SD_TotalCDR[1], Bstrap_Result$Avg_TotalReserve,1)))
Table_4 <- rbind(Table_4, Table_4_Totals)
dimnames(Table_4) <- list(c(1:length(Triangle), "Total"), c("Avg Reserves", "Bstrap SD", "Bstrap CoV %", "CDR SD", "CDR SD Ratio %"))
names(dimnames(Table_4)) <- c("Year","Simulated (Undiscounted)")
Table_4
```
<br><br>

### Table 5: Discounted simulation results summary, including summary statistics

```{r, message=FALSE}
# Table 5 - Discounted Results
disc_rate <- 0.03 # discount rate
offset <- 0.5 # assume payments are made half-way through the year
Bstrap_Result_Disc_Res <- Bstrap_Disc_Reserves(Bstrap_Result$Cumulatives, disc_rate, offset)
Table_5 <- cbind(round(Bstrap_Result_Disc_Res$Avg_Disc_Res), round(Bstrap_Result_Disc_Res$SD_Disc_Res), round(100*Bstrap_Result_Disc_Res$CoV_Disc_Res,1))
Table_5_Totals <- cbind(round(Bstrap_Result_Disc_Res$Avg_Disc_TotalRes), round(Bstrap_Result_Disc_Res$SD_Disc_TotalRes), round(100*Bstrap_Result_Disc_Res$Cov_Disc_TotalRes,1))
Table_5 <- rbind(Table_5, Table_5_Totals)
dimnames(Table_5) <- list(c(1:length(Triangle), "Total"), c("Avg Reserves", "Bstrap SD", "Bstrap CoV %"))
names(dimnames(Table_5)) <- c("Year","Simulated (Undiscounted)")
Table_5

# Show set of summary statistics from bootstrap results
ShowStats <- ShowSummaryStats(Bstrap_Result_Disc_Res, Output="Reserves")
```
<br><br>

### Histogram of total discounted reserves

```{r, message=FALSE}
# Histograms - Discounted reserves
plotHistogram_Total(Bstrap_Result_Disc_Res$TotalReserve)
#plotHistogram_by_yr(Bstrap_Result_Disc_Res$Reserves)
```
<br><br>

### Table 6: SDs of simulated CDRs for each future year

```{r}
#Table 6 - SDs of simulated CDRs for each future year
Table_6 <- t(CDR_Result$SD_CDR)
Table_6 <- rbind(Table_6,CDR_Result$SD_TotalCDR)
Table_6_SS <- Table_6 * Table_6
Table_6_SS <- sqrt(apply(Table_6_SS, 1,sum))
Table_6 <- cbind(round(Table_6), round(Table_6_SS))
dimnames(Table_6) <- list(c(1:length(Triangle), "Total"), c(1:(length(Triangle)-1), "Sqrt SS"))
names(dimnames(Table_6)) <- c("Year","SD(CDR) by Future Year")
Table_6
```
<br><br>

### Table 7: VaR @ 99.5% of simulated CDRs for each future year

```{r}
#Table 7 - VaR@99.5% of simulated CDRs for each future year
Table_7 <- t(CDR_Result$CDR_VAR)
Table_7 <- rbind(round(Table_7),round(CDR_Result$TotalCDR_VAR))
dimnames(Table_7) <- list(c(1:length(Triangle), "Total"), c(1:(length(Triangle)-1)))
names(dimnames(Table_7)) <- c("Year","VAR(CDR) @ 99.5% by Future Year")
Table_7
```
<br><br>

## Solvency II Cost-of-Capital Risk Margins
<br>

### Table 8: Cost-of-Capital Risk Margin

```{r}
# 
# Solvency II Cost-of-Capital Risk Margins
#
# All costs-of-Capital assumed to be in arrears and discounted a full year.
# (ie Offset=1 in CoC_RM function). Check Solvency II documentation.
#

#Table 8 - Cost-of-Capital Risk Margin
#RM_Initial_Capital <- 4867412 # the value used in the paper
CoC_rate <- 0.06
# Set initial capital
RM_Initial_Capital <- CDR_Result$TotalCDR_VAR[1]
# Caluclate discounted reserves at each future year (discounted back to that year)
Disc_Fut_Res <- Disc_Future_Reserves(Incrementals(Bstrap_Result$CL_Cumulatives), disc_rate, offset)
# Obtain "Capital Profile"
Disc_BE_Profile <- Capital_Profile(Disc_Fut_Res)
# Calculate cost-of-capital risk margin
Disc_RM_BE <- CoC_RM(RM_Initial_Capital, Disc_BE_Profile, CoC_rate, disc_rate, 1)

Table_8 <- cbind(round(Disc_Fut_Res), round(Disc_RM_BE$Capital), round(100*Disc_BE_Profile,1), round(Disc_RM_BE$CoC), round(Disc_RM_BE$Disc_CoC))
BE_basis_RM <- round(Disc_RM_BE$RM)
dimnames(Table_8) <- list(c(0:(length(Triangle)-2)), c("Disc Fut Res","Capital","Capital Profile %", "Cost of Capital", "Disc CoC"))
names(dimnames(Table_8)) <- c("Future Year","")
Table_8
names(BE_basis_RM) <- "Risk Margin (Best Estimate Basis)"
BE_basis_RM
```
<br><br>

### Table 9: Risk Margins under different bases

```{r}
# Table 9 - Risk Margins under different bases
CDR_SD_Profile <- Capital_Profile(CDR_Result$SD_TotalCDR)
CDR_VAR_Profile <- Capital_Profile(CDR_Result$TotalCDR_VAR)
Disc_RM_SD <- CoC_RM(RM_Initial_Capital, CDR_SD_Profile, CoC_rate, disc_rate, 1)
Disc_RM_VAR <- CoC_RM(RM_Initial_Capital, CDR_VAR_Profile, CoC_rate, disc_rate, 1)
Table_9_RMs <- cbind(round(Disc_RM_BE$RM), round(Disc_RM_SD$RM), round(Disc_RM_VAR$RM))
Table_9 <- cbind(round(Disc_RM_BE$Capital), round(Disc_RM_SD$Capital), round(Disc_RM_VAR$Capital))
Table_9 <- rbind(Table_9, Table_9_RMs)
dimnames(Table_9) <- list(c(0:(length(Triangle)-2),"Risk Margin"), c("Best Estimate","CDR SD","CDR VaR @ 99.5%"))
names(dimnames(Table_9)) <- c("Future Year","Risk Margins under different bases")
Table_9
```
<br><br>

## IFRS 17 Risk Adjustments
<br>

### Table 10: Risk adjustments using risk measures applied to the distribution of discounted reserves

```{r}
#Table 10 - Risk adjustments using risk measures applied to distribution of discounted reserves
VAR_level <- 0.75
TVAR_level <- 0.4
PHT_param <- 1.85

DiscTotalReserve_VAR <- -VAR(-Bstrap_Result_Disc_Res$TotalReserve, (1-VAR_level))
DiscTotalReserve_TVAR <- TVAR(Bstrap_Result_Disc_Res$TotalReserve, TVAR_level)
DiscTotalReserve_PHT <- PHT(Bstrap_Result_Disc_Res$TotalReserve, PHT_param)
DiscTotalReserve_VAR_RM <- DiscTotalReserve_VAR - Bstrap_Result_Disc_Res$Avg_Disc_TotalRes
DiscTotalReserve_TVAR_RM <- DiscTotalReserve_TVAR - Bstrap_Result_Disc_Res$Avg_Disc_TotalRes
DiscTotalReserve_PHT_RM <- DiscTotalReserve_PHT - Bstrap_Result_Disc_Res$Avg_Disc_TotalRes
DiscTotalReserve_VAR_RM_ratio <- DiscTotalReserve_VAR_RM/Bstrap_Result_Disc_Res$Avg_Disc_TotalRes
DiscTotalReserve_TVAR_RM_ratio <- DiscTotalReserve_TVAR_RM/Bstrap_Result_Disc_Res$Avg_Disc_TotalRes
DiscTotalReserve_PHT_RM_ratio <- DiscTotalReserve_PHT_RM/Bstrap_Result_Disc_Res$Avg_Disc_TotalRes
Table_10_R1 <- cbind(round(100*VAR_level), round(100*TVAR_level), round(100*PHT_param))
Table_10_R2 <- cbind(round(DiscTotalReserve_VAR_RM), round(DiscTotalReserve_TVAR_RM), round(DiscTotalReserve_PHT_RM))
Table_10_R3 <- cbind(round(Bstrap_Result_Disc_Res$Avg_Disc_TotalRes), round(Bstrap_Result_Disc_Res$Avg_Disc_TotalRes), round(Bstrap_Result_Disc_Res$Avg_Disc_TotalRes))
Table_10_R4 <- cbind(round(DiscTotalReserve_VAR), round(DiscTotalReserve_TVAR), round(DiscTotalReserve_PHT))
Table_10_R5 <- cbind(round(100*DiscTotalReserve_VAR_RM_ratio,1), round(100*DiscTotalReserve_TVAR_RM_ratio,1), round(100*DiscTotalReserve_PHT_RM_ratio,1))
Table_10 <- rbind(Table_10_R1, Table_10_R2, Table_10_R3, Table_10_R4, Table_10_R5)
dimnames(Table_10) <- list(c("Risk tolerance %", "Risk adjustment", "Best estimate (disc)", "Total", "Risk adjustment %"),
                           c("Value at Risk", "Tail Value at Risk","Prop. Hazards Transform"))
Table_10
```
<br><br>

### Table 11: Equivalent risk tolerance levels to give Risk Adjustment = Cost-of-Capital risk margin

```{r}
#Table 11 - Equivalent risk tolerance levels to give risk adjustment = Cost-of-Capital risk margin
RM <- BE_basis_RM
RM_ratio <- RM/Disc_Fut_Res[1]
AvgDiscTotalRes <- Bstrap_Result_Disc_Res$Avg_Disc_TotalRes
# Search for VAR, TVAR and PHT risk tolerance levels
target <- RM
VAR_level <- uniroot(function(p) -VAR(-Bstrap_Result_Disc_Res$TotalReserve,(1-p)) -
                       AvgDiscTotalRes - target, c(0.000001,1))
TVAR_level <- uniroot(function(p) TVAR(Bstrap_Result_Disc_Res$TotalReserve,p) - 
                        AvgDiscTotalRes - target, c(0,0.999999))
PHT_level <- uniroot(function(p) PHT(Bstrap_Result_Disc_Res$TotalReserve,p) - 
                       AvgDiscTotalRes -target, c(1,1000))

DiscTotalReserve_VAR <- -VAR(-Bstrap_Result_Disc_Res$TotalReserve, (1-VAR_level$root))
DiscTotalReserve_TVAR <- TVAR(Bstrap_Result_Disc_Res$TotalReserve, TVAR_level$root)
DiscTotalReserve_PHT <- PHT(Bstrap_Result_Disc_Res$TotalReserve, PHT_level$root)
DiscTotalReserve_VAR_RM <- DiscTotalReserve_VAR - AvgDiscTotalRes
DiscTotalReserve_TVAR_RM <- DiscTotalReserve_TVAR - AvgDiscTotalRes
DiscTotalReserve_PHT_RM <- DiscTotalReserve_PHT - AvgDiscTotalRes
DiscTotalReserve_VAR_RM_ratio <- DiscTotalReserve_VAR_RM/AvgDiscTotalRes
DiscTotalReserve_TVAR_RM_ratio <- DiscTotalReserve_TVAR_RM/AvgDiscTotalRes
DiscTotalReserve_PHT_RM_ratio <- DiscTotalReserve_PHT_RM/AvgDiscTotalRes

Table_11_R1 <- c(NA, sprintf("%1.2f%%", 100*VAR_level$root), sprintf("%1.2f%%", 100*TVAR_level$root),
                 sprintf("%1.0f%%",round(100*PHT_level$root)))
Table_11_R2 <- c(RM, DiscTotalReserve_VAR_RM, DiscTotalReserve_TVAR_RM, DiscTotalReserve_PHT_RM)
Table_11_R3 <- c(Disc_Fut_Res[1], rep(AvgDiscTotalRes, 3))
Table_11_R4 <- c((Disc_Fut_Res[1] + RM), DiscTotalReserve_VAR, DiscTotalReserve_TVAR, DiscTotalReserve_PHT)
Table_11_R5 <- c(RM_ratio, DiscTotalReserve_VAR_RM_ratio, DiscTotalReserve_TVAR_RM_ratio, DiscTotalReserve_PHT_RM_ratio)
Table_11 <- rbind(Table_11_R1, format(round(Table_11_R2), big.mark=","), format(round(Table_11_R3), big.mark=","), 
                  format(round(Table_11_R4), big.mark=","), sprintf("%1.2f%%", 100*Table_11_R5))
dimnames(Table_11) <- list(c("Risk tolerance", "Risk adjustment", "Best estimate (disc)", "Total", "Risk adjustment %"),
                           c("Cost-of-Capital", "Value at Risk", "Tail Value at Risk","Prop. Hazards Transform"))
Table_11
```
<br><br>

## Alternative bases for Solvency II Cost-of-Capital Risk Margins
<br>

### Table 12: Mean, SD and VaR of the discounted reserves (and SD of the undiscounted reserves) with associated CoC risk margins

```{r}
# Table 12 - Mean, SD and VaR of the discounted reserves (and SD of the undiscounted reserves) with CoC risk margins
Bstrap_Result_Disc <- Bstrap_Disc_Future_Reserves(Bstrap_Result$Cumulatives, disc_rate, offset)
Bstrap_Result_UnDisc <- Bstrap_Disc_Future_Reserves(Bstrap_Result$Cumulatives, 0, 0)
# Capital using VaR @ target and 99.5 percentile levels:
target1 <- CDR_Result$TotalCDR_VAR[1]
VAR_level_res <- uniroot(function(p) -VAR(-Bstrap_Result_Disc_Res$TotalReserve,(1-p)) -
                           Bstrap_Result_Disc_Res$Avg_Disc_TotalRes - target1, c(0.000001,1))
Disc_FutRes_VAR_root <- -apply(-Bstrap_Result_Disc$FutureReserves,2,VAR, p=(1-VAR_level_res$root)) - Bstrap_Result_Disc$Avg_Disc_Fut_Res
Disc_FutRes_VAR_995 <- -apply(-Bstrap_Result_Disc$FutureReserves,2,VAR, p=(1-0.995)) - Bstrap_Result_Disc$Avg_Disc_Fut_Res

#
RM_Initial_Capital_T12 <- Disc_FutRes_VAR_root[1]
Disc_AvgRes_RM <- CoC_RM(RM_Initial_Capital_T12, Capital_Profile(Bstrap_Result_Disc$Avg_Disc_Fut_Res), CoC_rate, disc_rate, 1)$RM
Disc_SDReS_RM <- CoC_RM(RM_Initial_Capital_T12, Capital_Profile(Bstrap_Result_Disc$SD_Disc_Fut_Res), CoC_rate, disc_rate, 1)$RM
UnDisc_SDReS_RM <- CoC_RM(RM_Initial_Capital_T12, Capital_Profile(Bstrap_Result_UnDisc$SD_Disc_Fut_Res), CoC_rate, disc_rate, 1)$RM
Disc_VARRes_RM_root <- CoC_RM(RM_Initial_Capital_T12, Capital_Profile(Disc_FutRes_VAR_root), CoC_rate, disc_rate, 1)$RM
# Using VaR@99.5% of discounted future reserves for initial capital and capital profile
Disc_VARRes_RM_995 <- CoC_RM(Disc_FutRes_VAR_995[1], Capital_Profile(Disc_FutRes_VAR_995), CoC_rate, disc_rate, 1)$RM

Table_12 <- cbind(round(Bstrap_Result_Disc$Avg_Disc_Fut_Res),round(Bstrap_Result_Disc$SD_Disc_Fut_Res),round(Bstrap_Result_UnDisc$SD_Disc_Fut_Res), round(Disc_FutRes_VAR_root),round(Disc_FutRes_VAR_995))
Table_12_RMs <- cbind(round(Disc_AvgRes_RM), round(Disc_SDReS_RM), round(UnDisc_SDReS_RM), round(Disc_VARRes_RM_root), round(Disc_VARRes_RM_995))
Table_12 <- rbind(Table_12, Table_12_RMs)
dimnames(Table_12) <- list(c(0:(length(Triangle)-2),"Risk Adjustment"),
        c("Avg(Disc Res)","SD(Disc Res)","SD(Undisc Res)",
          paste0("VaR(Disc Res)@", round(100*VAR_level_res$root,1), "%"), "VaR(Disc Res)@99.5%"))
names(dimnames(Table_12)) <- c("Future Year","Mean, SD, VaR of reserves with CoC risk adjustments")
Table_12
```
<br><br>

### Table 13: CoC risk margins based on reverse sum of CDRs

```{r}
# Table 13 - CoC risk margins based on reverse sum of CDRs
c1 <- Table_3[nrow(Table_3),2:(ncol(Table_3)-2)]
c1 <- as.vector(c1, "numeric")
CDRRevSum_SD_MW <- rev(sqrt(cumsum(rev(c1*c1))))

CDRRevSum <- CDR_Rev_Sum(CDR_Result$TotalCDR)
CDRRevSum_SD <- CDRRevSum$SD_RevSum_CDR

target2 <- CDR_Result$TotalCDR_VAR[1]
VAR_level_cdr <- uniroot(function(p) -VAR(CDRRevSum$RevSum_CDR[1,], (1-p)) + CDRRevSum$Avg_RevSum_CDR[1]
                         - target2, c(0.000001 ,1))
CDRRevSum_VAR_root <- -apply(CDRRevSum$RevSum_CDR,1,VAR, p=(1-VAR_level_cdr$root)) + CDRRevSum$Avg_RevSum_CDR
CDRRevSum_VAR_995 <- -apply(CDRRevSum$RevSum_CDR,1,VAR, p=(1-0.995)) + CDRRevSum$Avg_RevSum_CDR 
#
RM_Initial_Capital_T13 <- CDRRevSum_VAR_root[1]
CDRRevSum_SD_MW_RM <- CoC_RM(RM_Initial_Capital_T13, Capital_Profile(CDRRevSum_SD_MW), CoC_rate, disc_rate, 1)$RM
CDRRevSum_SD_RM <- CoC_RM(RM_Initial_Capital_T13, Capital_Profile(CDRRevSum_SD), CoC_rate, disc_rate, 1)$RM
CDRRevSum_VAR_RM_root <- CoC_RM(RM_Initial_Capital_T13, Capital_Profile(CDRRevSum_VAR_root), CoC_rate, disc_rate, 1)$RM
CDRRevSum_VAR_RM_995 <- CoC_RM(CDRRevSum_VAR_995[1], Capital_Profile(CDRRevSum_VAR_995), CoC_rate, disc_rate, 1)$RM

Table_13 <- cbind(round(CDRRevSum_SD_MW), round(CDRRevSum_SD), round(CDRRevSum_VAR_root), round(CDRRevSum_VAR_995))
Table_13_RMs <- cbind(round(CDRRevSum_SD_MW_RM), round(CDRRevSum_SD_RM), round(CDRRevSum_VAR_RM_root), round(CDRRevSum_VAR_RM_995))
Table_13 <- rbind(Table_13, Table_13_RMs)
dimnames(Table_13) <- list(c(0:(length(Triangle)-2),"Risk Adjustment"),
                           c("MW RMSEP","SD(Simulated)",paste0("VaR @ ", round(100*VAR_level_cdr$root,1),"%"),"VaR @ 99.5%"))
names(dimnames(Table_13)) <- c("Future Year","Risk adjustments based on Reverse sum of CDRs")
Table_13
```
<br><br>

### Fig 1: Capital Profiles associated with Table 9 (including VaR @ target% of discounted outstanding reserves)

```{r, message=FALSE, warning=FALSE}
# Fig 1 - Capital Profiles associated with Table 9 (including VaR @ target% of discounted outstanding reserves)
# put in alphabetical order for legend
a_profile <- Disc_BE_Profile
b_profile <- CDR_SD_Profile
c_profile <- CDR_VAR_Profile
d_profile <- Capital_Profile(Disc_FutRes_VAR_root)

Fig_1_Profiles <- tibble(date=c(0:(length(a_profile)-1)),a_profile, b_profile, c_profile, d_profile)
#Fig_1_Profiles # gives wide format. Long format needed for graph:
Fig_1_Profiles_long <- gather(Fig_1_Profiles, Method, Value, -"date")
Fig_1_theme <- theme(legend.title=element_blank(), plot.title = element_text(hjust=0.5), legend.position="bottom")
ggplot(Fig_1_Profiles_long, aes(x=date, y=Value*100, colour=Method, shape=Method)) +
  geom_line(size=1) + geom_point(size=1.8) +
  guides(shape=FALSE) +
  ggtitle("Fig 1. Capital Profiles by Year") +
  labs(y="Percent of Opening Capital",x="Future Year") +
  scale_color_hue(labels = c("Best estimate basis", "Standard deviation","VaR(CDR) @ 99.5%", 
                             paste0("VaR(Reserves) @ ", round(100*VAR_level_res$root,1),"%"))) +
  scale_x_continuous(breaks=c(0:(length(Triangle)-2))) +
  theme_bw() + Fig_1_theme
```
<br><br>

